```{r}```

# LME library examples

library(magrittr)
library(data.table)
library(survey)
library(lme4)

# import test pseudo-panel statistics

dt_eff <- fread("output/rentsbi.csv")

# transform data accordingly

dt_eff[, variable_num := 0][variable == "prop_ren_w", variable_num := 1][variable == "prop_ren_k", variable_num := 2][, years_bi := rep(1:7, 2)]
dt_mixed <- dt_eff[, list(years_bi, variable_num, value)]
setnames(dt_mixed,
    old = c("years_bi", "variable_num", "value"),
    new = c("year", "class", "rents")
)
dt_mixed$Covariate1 <- rbinom(n = nrow(dt_mixed), size = 10, prob = 0.2)

## estimate random correlated effects (Mixed Models)

# only effects, no covariates

fm1 <- lmer(rents ~ year + (year | class), data = dt_mixed)
fm1 %>%
    summary() %>%
    print()
print("-----------------------------")
fm1 %>% print()
print("-----------------------------")
print("-----------------------------")

# effects + one covariate/regressor

fm2 <- lmer(rents ~ year + Covariate1 + (year | class), data = dt_mixed)
fm2 %>%
    summary() %>%
    print()
print("-----------------------------")
fm2 %>% print()
print("-----------------------------")
print("-----------------------------")
dt <- "saves/eff-pool-2002-2020.csv" %>% fread() # Data table con microdatos anuales
years <- c(2002, 2005, 2008, 2011, 2014, 2017, 2020)
means <- list()
dt[, rentsbi := 0][rents > 0, 1 * renthog & rents > 1000]
for (i in seq_along(years)) {
    dt_yr <- dt[sv_year == years[i]] %>% data.frame()
    dt_sv <- svydesign(
        ids = ~1,
        data = dt_yr,
        weights = ~ dt_yr$facine3
    )
    means[[i]] <- svyby(~rentsbi, ~class, dt_sv, svymean)
}
print(means)

```{r}```
